A formalization of semi-simplicial and semi-cubical sets in dependent type theory

### 2023-01-10 paper/paper.tex
paper, art.cls: use conference mode, use IEEEtran bib
paper: minor polish

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, minted, rotating}
\usepackage[prefix=bonak]{art.cls/xkeymask}
\usepackage[skip=0.4em]{parskip}
\usetikzlibrary{patterns}

@@

% Universe, referred to as U
\newcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
\newcommandx{\HGpd}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HGpd}}_{#1}}}
\newcommand{\Type}{\ensuremath{\mathsf{\color{spanish-blue}{Type}}}}

@@

\NewEnviron{eqntable}[1]{
  \begin{table*}[t!]
    \small
    \begin{tabularx}{\linewidth}{@{}>{$}l<{$} >{$}c<{$} >{$}c<{$} >{$}Y<{$} @{}}
      \toprule
      \BODY
      \bottomrule
    \end{tabularx}
    \caption{#1}
  \end{table*}
}

@@

\title{A formalization of semi-simplicial and semi-cubical sets}
\author{
  Hugo Herbelin \\
  Université Paris Cité, Inria, CNRS, IRIF, Paris \\
  \and
  Ramkumar Ramachandra \\
  Université Paris Cité, Inria, CNRS, IRIF, Paris
}
\date{}

\color{gray65}

@@

\begin{align*}
  \layer[n][p](D)(d) & \defeq & \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \times \\
                     &        & \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
\end{align*}

@@

\begin{align*}
  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet     \\
  \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =_{HProp}      \\
  \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet     \\
  \ap \restrf[m][\epsilon][q][n][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
\end{align*}

@@

The upside of this definition is that all inequalities of the form $m \leq n$ are equivalent, definitionally. By placing the definition in \texttt{SProp}, we have definitional equality of inequality proofs. For the purpose of unification, however, this definition doesn't go far enough. Consider the unification problems:

@@

where \texttt{le\_trans} is transitivity, \texttt{le\_refl} is reflexivity, and \texttt{?p} is an existential variable. These two problems definitionally hold in \texttt{SProp}, but equalizing them does not solve the existential. For unification to be useful in inferring existentials, we present our next definition, which we dub as the ``Yoneda variant'':

@@

\newpage
\bibliographystyle{alpha}
\bibliography{paper}

>>>>

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, minted, rotating}
\usepackage[prefix=bonak]{art.cls/xkeymask}
\usetikzlibrary{patterns}

@@

% Universe, referred to as U
\newcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
\newcommandx{\HGpd}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HGpd}}_{#1}}}
\newcommand{\Type}{\ensuremath{\mathsf{\color{spanish-blue}{Type}}}}
\newcommand{\SProp}{\ensuremath{\mathsf{\color{spanish-blue}{SProp}}}}

@@

\NewEnviron{eqntable}[1]{
  \begin{table*}[!t]
    \small
    \begin{tabularx}{\linewidth}{@{}>{$}l<{$} >{$}c<{$} >{$}c<{$} >{$}Y<{$} @{}}
      \toprule
      \BODY
      \bottomrule
    \end{tabularx}
    \caption{#1}
  \end{table*}
}

@@

\title{A formalization of semi-simplicial and semi-cubical sets in dependent type theory}
\author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra} \IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}

@@

\begin{align*}
  \layer[n][p](D)(d) & \defeq & \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) & \times \\
                     &        & \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d)) &
\end{align*}

@@

\begin{align*}
  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet       \\
  \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet     \\
  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =_\mathit{HProp} \\
  \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet   \\
  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet       \\
  \ap \restrf[m][\epsilon][q][n][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
\end{align*}

@@

The upside of this definition is that all inequalities of the form $m \leq n$ are equivalent, definitionally. By placing the definition in \SProp, we have definitional equality of inequality proofs. For the purpose of unification, however, this definition doesn't go far enough. Consider the unification problems:

@@

where \texttt{le\_trans} is transitivity, \texttt{le\_refl} is reflexivity, and \texttt{?p} is an existential variable. These two problems definitionally hold in \SProp, but equalizing them does not solve the existential. For unification to be useful in inferring existentials, we present our next definition, which we dub as the ``Yoneda variant'':

@@

\bibliographystyle{IEEEtran}
\bibliography{paper}
